\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-06-08 doc/paper.tex
added another sentcence regarding additional solver.

In addition the modular design of FlexibleSUSY allows for the solver
for the boundary value problem to be replaced. An alternative solver
with better convergence properties (at the expense of slower speed) is
already planned for a later release.

>>>>

Finally instead of tinkering with the two-scale solver one may wish to replace it entirely. the modular design of FlexibleSUSY allows for the solver
for the boundary value problem to be replaced. An alternative solver
with better convergence properties (at the expense of slower speed) is
already planned for a later release.
